Hector Permafrost

### 2019-09-13 analysis/paper/paper.Rmd
Clean up captions, etc. in RMArkdown doc

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>"
)

@@

@@

f <- function(...) {
  here::here("analysis", "figures", ...)
}
```

@@

```{r param-density, echo = FALSE, fig.cap = param_density_cap}
param_density_cap <- paste(
  "Input parameter distributions for this analysis."
)
knitr::include_graphics(file_in(f("param-density.png")))
```

@@

```{r fig-global-timeseries, fig.cap = global_ts_cap, fig.dim = c(10, 8)}
global_ts_cap <- paste(
  "Time series of Hector outputs for different parameter combinations."
)
readd(ts_global_sims)
```

@@

```{r fig-global-scatter, fig.cap = global_scatter_cap, fig.dim = c(8, 5)}
global_scatter_cap <- paste(
  "Hector outputs at 2100 as a function of input parameter values."
)
readd(scatter_lastyear_global_sims)
```

@@

```{r fig-global-sensitivity, fig.cap = global_sensitivity_cap, fig.dim = c(5, 5)}
global_sensitivity_cap <- paste(
  "Sensitivity and variance decomposition analysis for global Hector."
)
readd(sensitivity_plot_sensitivity_global_params_lastyear_global_sims)
```

@@

```{r fig-biome-scatter, fig.cap = biome_scatter_cap, fig.dim = c(8, 8)}
biome_scatter_cap <- paste(
  "Hector outputs (with permafrost biome) at 2100 as a function of input parameter values."
)
readd(scatter_lastyear_biome_sims)
```

@@

```{r fig-biome-sensitivity, fig.cap = biome_sensitivity_cap, fig.dim = c(5, 7)}
biome_sensitivity_cap <- paste(
  "Sensitivity and variance decomposition analysis for Hector with permafrost biome."
)
readd(sensitivity_plot_sensitivity_biome_params_lastyear_biome_sims)
```

@@

```{r fig-global-dist, fig.cap = global_dist_cap}
global_dist_cap <- paste(
  "Input parameter distributions for global Hector."
)
# readd(draws_global_sims)
knitr::include_graphics(file_in(f("global_draws.png")))
```

@@

```{r fig-biome-dist, fig.cap = biome_dist_cap, fig.dim = c(9, 9)}
biome_dist_cap <- paste(
  "Input parameter distributions for Hector with biomes."
)
# readd(draws_biome_sims)
knitr::include_graphics(file_in(fig("biome_draws.png")))
```

>>>>

```{r setup, echo = FALSE}
library(drake)
library(knitr)
library(here)

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>"
)

@@

fig <- function(...) {
  filepath <- here("analysis", "figures", ...)
  knitr::include_graphics(file_in(filepath))
}

@@

m <- 0
htmlfig <- function() {
  m <<- m + 1
  out <- paste0("**Figure ", m, "**:")
  if (grepl("html", knitr::opts_knit$get("rmarkdown.pandoc.to"), ignore.case = TRUE)) {
    out
  } else {
    invisible(NULL)
  }
}
```

@@

```{r param-density, echo = FALSE, fig.cap = param_density_cap}
param_density_cap <- paste(
  htmlfig(),
  "Input parameter distributions for this analysis."
)
fig("param-density.png")
```

@@

```{r fig-global-timeseries, fig.cap = global_ts_cap, fig.dim = c(10, 8)}
global_ts_cap <- paste(
  htmlfig(),
  "Time series of Hector outputs for different parameter combinations."
)
readd(ts_global_sims)
```

@@

```{r fig-global-scatter, fig.cap = global_scatter_cap, fig.dim = c(8, 5)}
global_scatter_cap <- paste(
  htmlfig(),
  "Hector outputs at 2100 as a function of input parameter values."
)
readd(scatter_lastyear_global_sims)
```

@@

```{r fig-global-sensitivity, fig.cap = global_sensitivity_cap, fig.dim = c(5, 5)}
global_sensitivity_cap <- paste(
  htmlfig(),
  "Sensitivity and variance decomposition analysis for global Hector."
)
readd(sensitivity_plot_sensitivity_global_params_lastyear_global_sims)
```

@@

```{r fig-biome-scatter, fig.cap = biome_scatter_cap, fig.dim = c(8, 8)}
biome_scatter_cap <- paste(
  htmlfig(),
  "Hector outputs (with permafrost biome) at 2100 as a function of input parameter values."
)
readd(scatter_lastyear_biome_sims)
```

@@

```{r fig-biome-sensitivity, fig.cap = biome_sensitivity_cap, fig.dim = c(5, 7)}
biome_sensitivity_cap <- paste(
  htmlfig(),
  "Sensitivity and variance decomposition analysis for Hector with permafrost biome."
)
readd(sensitivity_plot_sensitivity_biome_params_lastyear_biome_sims)
```

@@

```{r fig-global-dist, fig.cap = global_dist_cap}
global_dist_cap <- paste(
  htmlfig(),
  "Input parameter distributions for global Hector."
)
# readd(draws_global_sims)
fig("global_draws.png")
```

@@

```{r fig-biome-dist, fig.cap = biome_dist_cap, fig.dim = c(9, 9)}
biome_dist_cap <- paste(
  htmlfig(),
  "Input parameter distributions for Hector with biomes."
)
# readd(draws_biome_sims)
fig("biome_draws.png")
```
